WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-02-17 article/Article.tex
add itk.class_ description
darcs-hash:20060217182957-2fc9d-d29bf24d5191d32d9a34f82bd3cd08a5ab7b2b38.gz

>>>>

  \item \verb$itk.class_( object )$ return the class of an object. The \verb$__class__$
attribute is often not what the user want with ITK. \verb$itk.class_$ is a convenient
function to get the class of an ITK object.

Note that it is called \verb$class_$ and not \verb$class$, because \verb$class$ is a
reseved word in python.

Example:
\begin{verbatim}
10> median.__class__
10> <class 'itkMedianImageFilter.itkMedianImageFilterIF2IF2_PointerPtr'>

11> itk.class_(median)
11> <class 'itkMedianImageFilter.itkMedianImageFilterIF2IF2'>
\end{verbatim}
